Introducing Statistical Design of Experiments to SPARQL Endpoint Evaluation

### 2013-05-08 exp1/iswc2013.tex
Table with p-values
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@526 43ef1190-90fd-4dd7-a769-d0121f02b80e

>>>>

While it is interesting to test the overall hypothesis that the new
implementation is an improvement, it is also interesting to know if
there are cases that it fails. Again, we treat the experiment as a
$2^5$ experiment replicated 8 times. Now, for each of the 16 resulting
combinations of the environmental factors for each level of
``Implement'', we extract 8 values. We may now run a t-test for each
of the replications, as above. The results are tabulated in
table~\ref{tab:pvaluesfull}. We see that there are significant
improvements in most cases, one may want to further investigate the
cases where they do not.

\begin{table}[ht]
\begin{center}
\caption{p-values for different parts of the experiment}\label{tab:pvaluesfull}
\begin{tabular}{ccccl}
  \hline
``TripleC'' & ``Lang'' & ``Union'' & ``Optional'' & $p$ \\ 
  \hline
  1 & 1 & 1 & 1 & 0.00032 \\ 
  1 & 1 & 1 & 2 & $2 \cdot 10^{-14}$ \\ 
  1 & 1 & 2 & 1 & $4.7 \cdot 10^{-14}$ \\ 
  1 & 1 & 2 & 2 & $2 \cdot 10^{-18}$ \\ 
  1 & 2 & 1 & 1 & $1.4 \cdot 10^{-06}$ \\ 
  1 & 2 & 1 & 2 & $8.3 \cdot 10^{-11}$ \\ 
  1 & 2 & 2 & 1 & 0.0017 \\ 
  1 & 2 & 2 & 2 & $2.1 \cdot 10^{-06}$ \\ 
  2 & 1 & 1 & 1 & 0.09 \\ 
  2 & 1 & 1 & 2 & $1.6 \cdot 10^{-09}$ \\ 
  2 & 1 & 2 & 1 & $8.4 \cdot 10^{-10}$ \\ 
  2 & 1 & 2 & 2 & $2.5 \cdot 10^{-13}$ \\ 
  2 & 2 & 1 & 1 & 0.29 \\ 
  2 & 2 & 1 & 2 & $9.1 \cdot 10^{-07}$ \\ 
  2 & 2 & 2 & 1 & 0.92 \\ 
  2 & 2 & 2 & 2 & 0.071 \\ 
   \hline
\end{tabular}
\end{center}
\end{table}
